Authors Response to Reviewer's Comments

### 2023-10-09 manuscript/review/authorsResponse.qmd
export pdf response to review

date: last-modified
link-citations: true
linkcolor: blue
number-sections: true
format: pdf
---

@@

@@

It is indeed interesting to account with the increasing data availability to better understand tree regeneration processes. However, we believe that the main take away it is not that it would be impossible to calibrate all 15 models against e.g. the EuFoRIa data to better capture regeneration, but that the focus should be in the study goals. And when the goal is to provide extrapolation into a future climate, then calibration against data under current climate may be unreliable. With the approach we have followed in this study where we have asked the models to simulate forest dynamics and capture regeneration without statistical predetermination we can better assess their behavior and understand how their current model structures and inclusion of exclusion of certain ecological processes impact the outputs we are seeing.

@@

### **COMMENT 17**

>>>>

date: last-modified
link-citations: true
linkcolor: blue
number-sections: true
format: 
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---

@@

### COMMENT 3

@@

It is indeed interesting to account with the increasing data availability to better understand tree regeneration processes. However, we believe that the main take away it is not that it would be impossible to calibrate all 15 models against e.g. the EuFoRIa data to better capture regeneration, but that the focus should be in the study goals. And when the goal is to provide extrapolation into a future climate, then calibration against data under current climate may be unreliable. With the approach we have followed in this study where we have asked the models to simulate forest dynamics and capture regeneration without statistical parametrisation we can better assess their behavior and understand how their current model structures and inclusion of exclusion of certain ecological processes impact the outputs we are seeing.

@@

### COMMENT 17
